Information Disclosure in Dynamic Innovation Contests

### 2025-05-23 paper/Paper.tex
update

%% Data: Submissions
The second component captures the submission events of each player $i$ to the system, denoted by the sequence $\{\hat{t}^i_k\}_{k=1}^{N_i}$.
Here, $N_i$ represents for the total number of submissions by player $i$, and $t$ represents for the time of each submission. 
We understand the submission events of player $i$ and $j$ as two conditional independent inhomogeneous Poisson processes, driven by the intensity functions $\tau_i(t)$ and $\tau_j(t)$.\footnote{That is, given the intensity functions $\tau_i(t)$ and $\tau_j(t)$, the submission events $\{\hat{t}^i_k\}_{k=1}^{N_i}$ and $\{\hat{t}^j_k\}_{k=1}^{N_i}$ are mutually independent.}
Then, during any time interval $\mathcal{S}$ of the contest duration $\mathcal{T}$, the Poisson arrival rate of submissions of the representative player $i$ is given by $\int_{s\in\mathcal{S}}\tau_i(s)ds$. 
We assume the submission intensity $\tau_i(t)$ is proportional to the effort level $m_i(\tilde{y}_t, t)$. More specifically, 
\begin{equation}\label{eq-model-intensity}
\tau_i(t) = r \cdot m_i(\tilde{y}_t, t)
\end{equation}
where $r>0$ is a tune parameter for the numerical robustness.

@@

We denote the set of unknown parameters by $\Theta := \{c_i, c_j, \sigma, \lambda, \mu_0\}$.
Once $\Theta$ is specified, the data-generating processes for $(y_t)$, $(\hat{y}_t)$, and $(\tilde{y}_t)$ are fully defined by equations (\ref{eq-state-dynamics}), (\ref{eq-leaderboard-gap}), and (\ref{eq-fintered-y-update}), although their realized trajectories remain stochastic.

@@

Our objective is to develop a Bayesian framework for inferring the unknown parameter set $\Theta := \{ c_i, c_j, \sigma, \lambda, \mu_0 \}$ using the data introduced above.

@@

\begin{lemma}\label{lmm-params-identifiability}
The contest parameters $c_i$, $c_j$, $\sigma$, $\lambda$ and $\mu_0$ are jointly identifiable. 
\end{lemma}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Synthetic Data}\label{tbl-contest90}
\begin{tabularx}{\textwidth}{lYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$} \\
\addlinespace[0.25ex]
\cline{2-6}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 2.0 & 1.0 & 0.0 \\
\midrule
 Posterior Mean    & 1.094 & 1.764 & 2.784 & 1.103 & 0.017 \\
 Posterior Std.       & 0.252 & 0.494 & 0.495 & 0.289 & 1.999 \\
 RMSE                  & 0.274 & 0.560 & 0.927 & 0.307 & 1.999 \\
 95\% Interval        
		& [0.691, 1.672] 
		& [1.013, 2.942]
		& [1.951, 3.878]
		& [0.618, 1.754] 
		& [-3.887, 3.886] \\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

Table~\ref{tbl-contest90} presents the Bayesian inference results based on the synthetic data that we display in Figure~\ref{fig-synthetic_90}. 
Due to the limited data from the short contest duration, the posterior distribution of some parameters (such as $\sigma$ in this example) remains relatively far from the true value.
Nevertheless, given the limited sample size, the performance of Bayesian estimation is satisfactory. 
For most parameters (specifically $c_i$, $c_j$, $\lambda$ and $\mu_0$), the posterior means lie reasonably close to their true values.

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Pooled Synthetic Data}\label{tbl-pool-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\addlinespace[0.25ex]
\cline{2-6}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 2.0 & 1.0 & 0.0\\
\midrule
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 5 Contests}} \\
Posterior Mean  & 1.215 & 1.647 & 1.969 & 1.079 &\\
Posterior Std.    & 0.120 & 0.178 & 0.143 & 0.130 &\\
RMSE               & 0.121 & 0.231 & 0.146 & 0.152 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 10 Contests}} \\
Posterior Mean  & 1.255 & 1.690 & 1.911 & 1.053 &\\
Posterior Std.    & 0.090 & 0.129 & 0.096 & 0.090 &\\
RMSE               & 0.105 & 0.230 & 0.131 & 0.105 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 20 Contests}} \\
Posterior Mean  & 1.206 & 1.639 & 1.981 & 0.990 &\\
Posterior Std.    & 0.059 & 0.090 & 0.069 & 0.059 &\\
RMSE               & 0.060 & 0.165 & 0.071 & 0.060 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Long Term Synthetic Data}\label{tbl-longterm-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\midrule
\multicolumn{5}{l}{\textbf{Contest of 6 Months}} \\
True Value           & 0.6     & 0.75   & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.840 & 0.835 & 1.944 & 1.142 &\\
Posterior Std.       & 0.138 & 0.152 & 0.226 & 0.245 &\\
RMSE                  & 0.276 & 0.174 & 0.233 & 0.283 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Contest of 12 Months}} \\
True Value           & 0.3     & 0.375 & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.307 & 0.341 & 2.187 & 1.034 &\\
Posterior Std.      & 0.020 & 0.033 & 0.127 & 0.098 &\\
RMSE                  & 0.021 & 0.047 & 0.226 & 0.102 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
(2) Players $i$ and $j$ submit 31 and 40 times in the 6-month contest, and 143 and 182 times in the 12-month contest, respectively.
}
\end{minipage}
\end{table}

@@

First, we estimate submission intensities $\tau_i(t)$ and $\tau_j(t)$ by kernel density estimation (KDE). 
Having $\hat{\tau}_i$ and $\hat{\tau}_j$, the effort levels of the two players are simply $m_i(t) = \hat{\tau}_i / r$ and $m_j(t) = \hat{\tau}_j / r$ by (\ref{eq-model-intensity}), where $r$ is the ratio of effort level and submission intensity. 
Next, with the submission times denoted by $\{t_k\}$, we have $y_{t_{k+1}} - y_{t_k} \sim \mathcal{N}\left(\frac{1}{r}\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds, \sigma^2(t_{k+1}-t_k)\right)$ by the dynamic of private leaderboard (\ref{eq-state-dynamics}). 
Then, by (\ref{normal-mle-r}) and (\ref{normal-mle-sigma}), we can estimate the parameters $r$ and $\sigma^2$ using MLE, that is  
\begin{equation*}
r^{\text{MLE}} = \frac{\sum_k\left[\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds\right]^2/(t_{k+1}-t_k)}{\sum_k(y_{t_{k+1}}-y_{t_k})\left[\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds\right] / (t_{k+1}-t_k)}
\end{equation*}
\begin{equation*}
\sigma^{\text{MLE}} = \frac{1}{n}\sum_k\frac{\left[y_{t_{k+1}}-y_{t_k}-\frac{1}{\hat{r}}\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds\right]^2}{t_{k+1}-t_k}
\end{equation*}

@@

\subsection{MLE for Normal Distribution}

Suppose we observe independent data points \( X_1, ..., X_n \), where each \( X_k \sim \mathcal{N}(M_k / r, \sigma^2 T_k) \) with known constants \( M_k \) and \( T_k \). 
The goal is to estimate the parameters \( r \) and \( \sigma \) via maximum likelihood estimation (MLE).
Ignoring constant terms, the log-likelihood function of the observed data is
\[
\ell(r, \sigma^2) = - \frac{n}{2} \log(\sigma^2) - \frac{1}{2\sigma^2} \sum_{k=1}^n \frac{\left( X_k - M_k/r \right)^2}{T_k}.
\]
To Estimate $r$, we expand the summation of second term and have 
\[
Q(r) = \sum_{k=1}^n \left( \frac{X_k^2}{T_k} - \frac{2X_k M_k}{r T_k} + \frac{M_k^2}{r^2 T_k} \right)
= A - \frac{2B}{r} + \frac{C}{r^2},
\]
where \( A = \sum X_k^2/T_k \), \( B = \sum X_k M_k/T_k \), and \( C = \sum M_k^2/T_k \). Taking the derivative with respect to \( r \) and setting it to zero gives:
\begin{equation}\label{normal-mle-r}
\frac{dQ}{dr} = \frac{2B}{r^2} - \frac{2C}{r^3} = 0 \quad \Rightarrow \quad \hat{r} = \frac{C}{B} = \frac{\sum M_k^2/T_k}{\sum X_k M_k/T_k}.
\end{equation}
Then, substituting \( \hat{r} \) back into the likelihood, the MLE for \( \sigma^2 \) is obtained by maximizing
\[
\ell(\sigma^2) = -\frac{n}{2} \log(\sigma^2) - \frac{1}{2\sigma^2} \sum_{k=1}^n \frac{\left( X_k - M_k/\hat{r} \right)^2}{T_k},
\]
which yields
\begin{equation}\label{normal-mle-sigma}
\hat{\sigma}^2 = \frac{1}{n} \sum_{k=1}^n \frac{\left( X_k - M_k/\hat{r}\right)^2}{T_k}.
\end{equation}

>>>>

%% Data: Submissions
The second component captures the submission events of each player $i$ to the system, denoted by the sequence $\{\hat{t}^i_k\}_{k=1}^{N_i}$.
Here, $N_i$ represents for the total number of submissions by player $i$, and $t$ represents for the time of each submission. 
We understand the submission events of player $i$ and $j$ as two conditional independent inhomogeneous Poisson processes, driven by the intensity functions $\tau_i(t)$ and $\tau_j(t)$.\footnote{That is, given the intensity functions $\tau_i(t)$ and $\tau_j(t)$, the submission events $\{\hat{t}^i_k\}_{k=1}^{N_i}$ and $\{\hat{t}^j_k\}_{k=1}^{N_i}$ are mutually independent.}
Then, during any time interval $\mathcal{S}$ of the contest duration $\mathcal{T}$, the Poisson arrival rate of submissions of the representative player $i$ is given by $\int_{s\in\mathcal{S}}\tau_i(s)ds$. 
We assume the submission intensity $\tau_i(t)$ is proportional to the effort level $m_i(\tilde{y}_t, t)$. More specifically, 
\begin{equation}\label{eq-model-intensity}
\tau_i(t) = r \cdot m_i(\tilde{y}_t, t)
\end{equation}
where $r>0$ is the ratio of submission intensity and effort level. 
The contest players are aware of this ratio, but the contest designer must infer it from the data.

@@

We denote the set of unknown parameters by $\Theta := \{c_i, c_j, r, \sigma, \lambda, \mu_0\}$.
Once $\Theta$ is specified, the data-generating processes for $(y_t)$, $(\hat{y}_t)$, and $(\tilde{y}_t)$ are fully defined by equations (\ref{eq-state-dynamics}), (\ref{eq-leaderboard-gap}), and (\ref{eq-fintered-y-update}), although their realized trajectories remain stochastic.

@@

Our objective is to develop a Bayesian framework for inferring the unknown parameter set $\Theta := \{ c_i, c_j, r, \sigma, \lambda, \mu_0 \}$ using the data introduced above.

@@

\begin{lemma}\label{lmm-params-identifiability}
The contest parameters $c_i$, $c_j$, $r$, $\sigma$, $\lambda$ and $\mu_0$ are jointly identifiable. 
\end{lemma}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Synthetic Data}\label{tbl-contest90}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$} \\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0 \\
\midrule
 Posterior Mean    & 1.078 & 1.711 & 14.645 & 2.777 & 1.103 & -0.010 \\
 Posterior Std.       & 0.382 & 0.661 & 3.986 & 0.503 & 0.303 & 2.026 \\
 RMSE                  & 0.401 & 0.694 & 4.002 & 0.925 & 0.320 & 2.026 \\
 95\% Interval        
		& [0.55, 1.99] 
		& [0.77, 3.30]
		& [7.8, 23.0]
		& [1.94, 3.93]
		& [0.61, 1.79] 
		& [-3.97, 4.00] \\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

Table~\ref{tbl-contest90} presents the Bayesian inference results based on the synthetic data that we display in Figure~\ref{fig-synthetic_90}. 
Due to the limited data from the short contest duration, the posterior distribution of some parameters (such as $\sigma$ in this example) remains relatively far from the true value.
Nevertheless, given the limited sample size, the performance of Bayesian estimation is satisfactory. 
For most parameters (specifically $c_i$, $c_j$, $r$, $\lambda$ and $\mu_0$), the posterior means lie reasonably close to their true values.

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Pooled Synthetic Data}\label{tbl-pool-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0\\
\midrule
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 5 Contests}} \\
Posterior Mean  & 1.215 & 1.647 && 1.969 & 1.079 &\\
Posterior Std.    & 0.120 & 0.178 && 0.143 & 0.130 &\\
RMSE               & 0.121 & 0.231 && 0.146 & 0.152 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 10 Contests}} \\
Posterior Mean  & 1.255 & 1.690 && 1.911 & 1.053 &\\
Posterior Std.    & 0.090 & 0.129 && 0.096 & 0.090 &\\
RMSE               & 0.105 & 0.230 && 0.131 & 0.105 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 20 Contests}} \\
Posterior Mean  & 1.206 & 1.639 && 1.981 & 0.990 &\\
Posterior Std.    & 0.059 & 0.090 && 0.069 & 0.059 &\\
RMSE               & 0.060 & 0.165 && 0.071 & 0.060 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Long Term Synthetic Data}\label{tbl-longterm-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\midrule
\multicolumn{5}{l}{\textbf{Contest of 6 Months}} \\
True Value           & 0.6     & 0.75   & 15.0 & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.840 & 0.835 & . & 1.944 & 1.142 &\\
Posterior Std.       & 0.138 & 0.152 & . & 0.226 & 0.245 &\\
RMSE                  & 0.276 & 0.174 & . & 0.233 & 0.283 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Contest of 12 Months}} \\
True Value           & 0.3     & 0.375 & . & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.307 & 0.341 & . & 2.187 & 1.034 &\\
Posterior Std.      & 0.020 & 0.033 & . & 0.127 & 0.098 &\\
RMSE                  & 0.021 & 0.047 & . & 0.226 & 0.102 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
(2) Players $i$ and $j$ submit 31 and 40 times in the 6-month contest, and 143 and 182 times in the 12-month contest, respectively.
}
\end{minipage}
\end{table}

@@

First, we estimate submission intensities $\tau_i(t)$ and $\tau_j(t)$ by kernel density estimation (KDE). 
Having $\hat{\tau}_i$ and $\hat{\tau}_j$, the effort levels of the two players are simply $m_i(t) = \hat{\tau}_i / r$ and $m_j(t) = \hat{\tau}_j / r$ by (\ref{eq-model-intensity}), where $r$ is the ratio of effort level and submission intensity. 
Next, with the submission times denoted by $\{t_k\}$, we have $y_{t_{k+1}} - y_{t_k} \sim \mathcal{N}\left(\frac{1}{r}\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds, \sigma^2(t_{k+1}-t_k)\right)$ by the dynamic of private leaderboard (\ref{eq-state-dynamics}). 
Then, by (\ref{normal-mle-sigma}), we can estimate the parameters $\sigma$ using MLE: 
\begin{equation*}
\sigma^{\text{MLE}} = \left(\frac{1}{n}\sum_k\frac{\left[y_{t_{k+1}}-y_{t_k}-\frac{1}{\hat{r}}\int^{t_{k+1}}_{t_k}\hat\tau_i(s) - \hat\tau_j(s)ds\right]^2}{t_{k+1}-t_k}\right)^{1/2}
\end{equation*}
where $\hat{r}$ is the Bayesian estimate.

@@

\subsection{MLE for $r$ and $\sigma^2$}

Suppose we observe independent data points \( X_1, ..., X_n \), where each \( X_k \sim \mathcal{N}(M_k / r, \sigma^2 T_k) \) with known constants \( M_k \) and \( T_k \). 
The goal is to estimate the parameters \( r \) and \( \sigma \) via maximum likelihood estimation (MLE).
Ignoring constant terms, the log-likelihood function of the observed data is
\[
\ell(r, \sigma^2) = - \frac{n}{2} \log(\sigma^2) - \frac{1}{2\sigma^2} \sum_{k=1}^n \frac{\left( X_k - M_k/r \right)^2}{T_k}.
\]
To estimate $r$, we expand the summation of second term and have 
\[
Q(r) = \sum_{k=1}^n \left( \frac{X_k^2}{T_k} - \frac{2X_k M_k}{r T_k} + \frac{M_k^2}{r^2 T_k} \right)
= A - \frac{2B}{r} + \frac{C}{r^2},
\]
where \( A = \sum X_k^2/T_k \), \( B = \sum X_k M_k/T_k \), and \( C = \sum M_k^2/T_k \). Taking the derivative with respect to \( r \) and setting it to zero gives:
\begin{equation}\label{normal-mle-r}
\frac{dQ}{dr} = \frac{2B}{r^2} - \frac{2C}{r^3} = 0 \quad \Rightarrow \quad \hat{r} = \frac{C}{B} = \frac{\sum M_k^2/T_k}{\sum X_k M_k/T_k}.
\end{equation}
Then, substituting \( \hat{r} \) back into the likelihood, the MLE for \( \sigma^2 \) is obtained by maximizing
\[
\ell(\sigma^2) = -\frac{n}{2} \log(\sigma^2) - \frac{1}{2\sigma^2} \sum_{k=1}^n \frac{\left( X_k - M_k/\hat{r} \right)^2}{T_k},
\]
which yields
\begin{equation}\label{normal-mle-sigma}
\hat{\sigma}^2 = \frac{1}{n} \sum_{k=1}^n \frac{\left( X_k - M_k/\hat{r}\right)^2}{T_k}.
\end{equation}
